### 2020-02-10 defesa/tex/chapter/e3p.tex
wip

\begin{figure}
	\centering
	\caption{Transforming a solution of E3P into a solution of the circumradius problem.}
	\includegraphics[scale=.43]{tex/figures/circumscribed-circle}
	\fautor
	\label{fig:circumscribed-circle}
\end{figure}

@@

To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}. There is no guarantee that this method will choose $n$ such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$. Nonetheless, in practice, it is considered to be a good estimate for the error

\begin{equation}
r_n = \max_{0 \le \theta < \pi} |f_n(\theta) - \xi(\theta)|,
\end{equation}
which measures how far the interpolation is at the point it worst approximates.

\subsection{Testing different interpolant degrees}

In this section, we run some experiments to verify how big the interpolation degree must be for good precision to be achieved. 
The interpolation was run for several degrees, for every triplet of points in an instance from \citeonline{canbolat}. We considered the error to be $|\xi(\hat{\theta})|$ for every root $\hat{\theta}$ found.

The results are shown in \autoref{fig:interpolant_error}, where the worst error found among every root is plotted against the interpolant degree. To improve accuracy while keeping the interpolation degree low, we took a suggestion from \citeonline{boyd:2013}, and divided  $[0, \pi)$ into $K$ sub-intervals. That way, $K$ interpolations are used to obtain every root in the whole interval. It can be seen in \autoref{fig:interpolant_error} that this strategy helps a lot in improving the accuracy even when degrees around $8$ are used.

\begin{figure}
	\centering
	\caption{The interpolation error measured on roots that were found.}
	\includegraphics[scale=.84]{tex/figures/interpolant_error}
	\fautor
	\label{fig:interpolant_error}
\end{figure}

@@

A complex polynomial can be obtained from $\xi$ by using an idea published in \citeonline{boyd:2006}. There, the author uses the identities
\begin{align}\label{eq:complex_trig}
	\cos{\theta} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
	\sin{\theta} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i},
\end{align}
which relate complex numbers with trigonometric functions, to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials.
This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial -- more details about this can be found in \citeonline{weidner}, where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.

@@

\begin{figure}[H]
	\centering
	\caption{An instance of E3P with four solutions.}
	\includegraphics[scale=.35]{tex/figures/e3p_4sols}
	\fautor
	\label{fig:e3p_4sols}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\caption{An instance of E3P with six solutions.}
	\includegraphics[scale=.35]{tex/figures/e3p_6sols}
	\fautor
	\label{fig:e3p_6sols}
\end{figure}

>>>>

\begin{figure}
	\centering
	\caption{Transforming a solution of E3P into a solution of the circumradius problem.}
	\includegraphics[scale=.5]{tex/figures/circumscribed-circle}
	\fautor
	\label{fig:circumscribed-circle}
\end{figure}

@@

To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}. There is no guarantee that this method will choose $n$ such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$. Nonetheless, in practice, it is considered to be a good estimate for the error
\begin{equation}
r_n = \max_{0 \le \theta < \pi} |f_n(\theta) - \xi(\theta)|,
\end{equation}
which measures how far the interpolation is at the point it worst approximates. 
\clearpage
\subsection{Testing different interpolant degrees}

In this section, we describe the results of an experiment we made to verify the accuracy of solutions found by the Chebyshev Interpolation method for different interpolation degrees. 
The main reason for doing this experiment was to obtain a practical lower-bound for the interpolation degree, which can be used later to decide whether to use this method or not. We also investigate if dividing the interpolation interval into $K$ sub-intervals, which is a suggestion given in \citeonline{boyd:2013}, yields an improvement in the accuracy of solutions.

Let $\delta : \R^2 \to \R_{>0}$ be a function defined as the left-hand-side of \autoref{eq:rotated_ellipse}, then, for an instance of E3P with three points $u, v, w$, we define the error of a solution as $$\max\{|\delta(u)|, |\delta(v)|, |\delta(w)| \}.$$
We created instances of E3P taking every triplet of points, and every ellipse from an MCE's instance named CM3 proposed in \citeonline{canbolat}. We also tried dividing the interval $[0, \pi]$ into a different number of sub-intervals taking $K \in\{1, 2, 4, 8\}$.

\begin{figure}
	\centering
	\caption{The maximum interpolation error.}
	\includegraphics[scale=.9]{tex/figures/error_roots}
	\fautor
	\label{fig:interpolant_error}
\end{figure}

In \autoref{fig:interpolant_error}, for each $K$, the maximum error observed among every instance of E3P for each interpolation degree is shown. It may be stated that adopting the strategy of dividing the interpolation interval into $K$ sub-intervals provides a significant improvement in accuracy.

Also, as expected, in \autoref{fig:last-coeff}, using the same instances, we were able to observe that the maximum absolute value of the last coefficient among every instance has the same behavior as its corresponding error in \autoref{fig:interpolant_error}.

\begin{figure}
	\centering
	\caption{The maximum absolute value of the last coefficient interpolation.}
	\includegraphics[scale=.9]{tex/figures/last_coeff}
	\fautor
	\label{fig:last-coeff}
\end{figure}

Assuming that $K=4$, we can say that for a small error to be achieved, we need to take an interpolation degree of at least $10$, increasing it based on the last coefficient rule. A suggestion in \citeonline{boyd:2013} says that if the last coefficient is not small, the interpolation degree must be doubled. 
This is only a suggestion of how to approach the problem of choosing a good interpolation degree. 
This procedure could still fail as a small last coefficient does not necessarily imply a small error everywhere in the interpolation interval.

@@

A complex polynomial can be obtained from $\xi$ by using an idea published in \citeonline{boyd:2006}. There, the author uses the identities

\begin{align}\label{eq:complex_trig}
	\cos{\theta} &= \dfrac{e^{i\theta} + e^{-i\theta}}{2}\\
	\sin{\theta} &= \dfrac{e^{i\theta} - e^{-i\theta}}{2i},
\end{align}
which relate complex numbers with trigonometric functions, to convert real trigonometric polynomials, which is the case of $\xi$, into univariate complex polynomials.
This approach is preferable as it preserves the numerical stability of the original real trigonometric polynomial -- more details about this can be found in \citeonline{weidner}, where it is said that computing the roots of a real trigonometric polynomial through this transformation does not yield loss of accuracy.

@@

\begin{figure}
	\centering
	\caption{An instance of E3P with four solutions.}
	\includegraphics[scale=.35]{tex/figures/e3p_4sols}
	\fautor
	\label{fig:e3p_4sols}
\end{figure}

@@

\begin{figure}
	\centering
	\caption{An instance of E3P with six solutions.}
	\includegraphics[scale=.35]{tex/figures/e3p_6sols}
	\fautor
	\label{fig:e3p_6sols}
\end{figure}

### 2020-02-10 defesa/tex/chapter/mcer.tex
wip

	\begin{equation}
	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
	\end{equation}
\end{definicao}

@@

\begin{lema}\label{lema:3pnts}
Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|>2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.

@@

	Let $w\in \Pp \cap E_j(q_j^*, \theta_j^*) \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}. Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$.

	For all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j^*) < 0$ as they are covered by the $j$-th ellipse.
	Then, to evaluate $f_w$ for every center and feasible angle that maintains $u$ and $v$ on $E_j$'s border, we introduce a new function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$, which is defined as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
	As $f_w$ and $\delta$ are continuous functions, $g_w$ is also continuous.

	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>1$. Then, by continuity, another angle $\bar{\theta} \in \Phi_j(u,v)$ must exist, such that $g_w(\bar{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis. The same can be said about the case where there exists an angle $\theta \in \Phi_j(u,v)$, such that a point $w \in \Pp \setminus E_j(q_j^*, \theta_j^*)$ enters the coverage of $E_j(\delta(\theta), \theta)$.
\end{proof}

@@

What \autoref{lema:3pnts} is saying is that, for every ellipse in an instance of MCER, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored. Because of that, it will be shown that we can construct a CLS which is finite and also contains an optimal solution.

@@

Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. We will define a set $\Omega(\Pp, \Ww, \Rr)$ and show that there exists an equivalent solution $(Q', \Theta')$ to  $(Q^*, \Theta^*)$, such that $(Q', \Theta') \in \Omega(\Pp, \Ww, \Rr)$. This is the same thing as showing that $\Omega(\Pp, \Ww, \Rr)$ contains an optimal solution for the instance $(\Pp, \Ww, \Rr)$.
The whole set $\Omega(\Pp, \Ww, \Rr)$ is constructed from a set of solutions for every ellipse. Let $j\in\{1, \dots, m\}$, we denote by $S_j$ the CLS for the $j$-th ellipse; its construction is broken into three separated cases denoted by $S_j^{(1)}$, $S_j^{(2)}$, and $S_j^{(3)}$. Next, we define them precisely.

@@

This is the case where $|E_j(q_j^*, \theta_j^*)|=1$, that is, the $j$-th ellipse only covers one point. 
This case is not treated by any of the previous results presented in this chapter. Nevertheless, taking this possibility into account can be done by including solutions in $S_j$ that are guaranteed to cover at least one point. This is represented by
\begin{equation}
	S_j^{(1)} = \bigcup_{u \in \Pp} \{(u, 0)\}.
\end{equation}

\subsection{Second case}

The second and third cases are addressed by \autoref{lema:3pnts}. 
Consider the second case to be the one where the $j$-ellipse covers more than one point and there is no equivalent solution with three points on the its border. 
By \autoref{lema:3pnts}, $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v$ on the ellipse's border, and is rotated by some angle in $\Phi_j(u,v)$. 
As only one angle is needed, we define $\theta_{uv}$ as the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
Having said that, we refer to $S_j^{(2)}$ the set of possible solutions that takes this case into account; we define it as
\begin{equation}
S_j^{(2)} = \bigcup_{\{u, v\} \subset \Pp} \{(q, \theta_{uv})\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \theta_{uv})\}.\\
\end{equation}
For a pair of points $u, v$, determining every ellipse with a fixed rotation angle that has $u$ and $v$ on its border is equivalent to determining the intersection points of two axis-parallel ellipses with the same shape parameters. This problem is discussed with great detail in \autoref{section:ellipses_intersection}.

@@

Finally, we define the CLS for the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$, and the set of possible solutions of an instance of MCER as
\begin{equation}\label{eq:omega}
\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\}.
\end{equation}

\begin{theorem}\label{th:mcer}
	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}. Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.	
\end{theorem}

>>>>

	\begin{equation}
	\Phi_j(u, v) := \{\theta \in [0, \pi) : \theta \textnormal{ is a } (E_j,u,v)\textnormal{-feasible angle}\}.
	\end{equation}
	We also refer to $\tilde{\Phi}_j(u,v)$ as the angle which makes $E_j$'s major-axis be parallel to the line that passes through $u$ and $v$. Note that if $\Phi_j(u,v) \neq \emptyset$, then $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$.
\end{definicao}

@@

\begin{lema}\label{lema:3pnts}
Let $(Q^*, \Theta^*)$ be an optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER; $j\in\{1, \dots, m\}$, such that $|\Pp \cap E_j(q_j^*, \theta_j^*)|\ge2$; $(Q', \Theta')\in\Pi(Q^*, \Theta^*)$; and $\{u, v\}\subset \partial E_j(q_j', \theta_j')$.

@@

	Let $w\in \Pp \setminus \{u,v\}$, then we define $f_w  : \R^2 \times [0, \pi) \mapsto \R_{\ge0}$ to be a function that takes a center $q \in \R^2$ and an angle of rotation $\theta\in [0, \pi)$, and returns the elliptical distance between $w$ and $E_j(q, \theta)$ minus $1$ as defined by the left-and-side of \autoref{eq:rotated_ellipse}. Keep in mind that, for all $w\in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus \{u,v\}$, we have that $f_w(q_j', \theta_j') < 0$ as they are covered by the $j$-th ellipse.

	Then, to evaluate $f_w$ for every center and feasible angle that maintains $u$ and $v$ on $E_j$'s border, we introduce a new function $g_w\colon \Phi_j(u,v) \mapsto \R_{\ge0}$, which is defined as $g_w(\theta) = f_w(\delta(\theta), \theta)$.
	As $f_w$ and $\delta$ are both continuous functions, $g_w$ is also continuous.

	Therefore, for any $\theta\in\Phi_j(u,v)$, if a point $w \in \Pp \cap E_j(q_j^*, \theta_j^*)\setminus\{u,v\}$ is not covered by $E_j(\delta(\theta), \theta)$, it must have $g_w(\theta)>0$. Then, by continuity, another angle $\bar{\theta} \in \Phi_j(u,v)$ must exist, such that $g_w(\bar{\theta})=1$, which means that $w\in \partial E_j(\delta(\hat{\theta}), \hat{\theta})$, contradicting the hypothesis. The same can be said about the case where there exists an angle $\theta \in \Phi_j(u,v)$, such that a point $w \in \Pp \setminus E_j(q_j^*, \theta_j^*)$ enters the coverage of $E_j(\delta(\theta), \theta)$.
\end{proof}

@@

What \autoref{lema:3pnts} is saying is that, for every ellipse in an instance of MCER, unless an equivalent optimal solution with three points on its border exits, the angle of rotation can practically be ignored. Because of that, it will be shown that we can construct a CLS for each ellipse which is finite and also contains an optimal solution.

@@

Let $(Q^*, \Theta^*)$ be any optimal solution of an instance $(\Pp, \Ww, \Rr)$ of MCER. We will define a set of solutions $\Omega(\Pp, \Ww, \Rr)$ and show that there exists an equivalent solution $(Q', \Theta')$ to  $(Q^*, \Theta^*)$, such that $(Q', \Theta') \in \Omega(\Pp, \Ww, \Rr)$. This is the same thing as showing that $\Omega(\Pp, \Ww, \Rr)$ for sure contains an optimal solution for the instance $(\Pp, \Ww, \Rr)$.
Before that, we introduce a definition for the CLS of every ellipse, which is then used to construct the set of solutions $\Omega(\Pp, \Ww, \Rr)$.

\begin{definicao}\label{def:Sj}
	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER. Then, for all $j\in\{1, \dots, m\}$, we define the \sigla{CLS}{Candidate Locations Set} of the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$ with
	\begin{align}
		S_j^{(1)} &= \bigcup_{u \in \Pp} \{(u, 0)\}\\
		S_j^{(2)} &= \bigcup_{\{u, v\} \subset \Pp} \{(q, \tilde{\Phi}_j(u,v))\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \tilde{\Phi}_j(u,v))\}\\
		S_j^{(3)} &= \bigcup_{\{u, v, w\} \subset \Pp} \{(q, \theta)\in \R^2\times\R: \{u, v, w\} \subset \partial E_j(q, \theta)\}.
	\end{align}
\end{definicao}

This definition breaks the construction of the CLS $S_j$ into three separated cases. The first one, $S_j^{(1)}$, represents solutions where the $j$-th ellipse covers only one point. The second one, $S_j^{(2)}$, takes into account solutions where the $j$-th ellipse covers at least two points, and no equivalent solution with three points on the ellipse's border exists. The last case, $S_j^{(3)}$, considers solutions where there exists an equivalent one with three points on the $j$-th ellipse's border. Following this, we move forward and introduce the main result of this section.

\begin{theorem}\label{th:mcer}
	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined as 
	\begin{equation*}\label{eq:omega}
	\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\},
	\end{equation*}
Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.
\end{theorem}
\begin{proof}
	The first thing to notice is that $\Omega(\Pp, \Ww, \Rr)$ is defined as the combination of every possible solution from each CLS. To prove that it contains an optimal solution $(Q^*, \Theta^*)$, we only need to prove that for all $j\in\{1, \dots, m\}$, there exists $(q_j, \theta_j)\in S_j$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) \subset \Pp \cap E_j(q_j, \theta_j)$. That is, we only need to show that the CLS of every ellipse contains a center and angle of rotation that makes the ellipse cover the same points (possibly some additional ones) that it covers in an optimal solution. To do that, we use \autoref{lema:3pnts} and break the possible optimal solutions into three cases.

	 In the first case, we consider solutions where the $j$-th ellipse covers less than one point, that is, $|\Pp \cap E_j(q_j^*, \theta_j^*)|\le1$. It is possible to see that $S_j^{(1)}$ takes this possibility into account as it includes in $\Omega(\Pp, \Ww, \Rr)$ every solution that has an ellipse centered at a point from $\Pp$.

	In the second case, we consider solutions where the $j$-th ellipse covers at least two points, and no equivalent solution exists, such that three points are on its border. This case is addressed by \autoref{lema:3pnts}, which says that an optimal solution $(Q^*, \Theta^*)$ of this type has equivalent solutions with two points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse's border, for any angle of rotation $\theta_j \in \Phi_j(u, v)$.
	As $\tilde{\Phi}_j(u,v) \in \Phi_j(u,v)$, we have that there exists $(q_j, \theta_j) \in S_j^{(2)}$, such that $\Pp \cap E_j(q_j^*, \theta_j^*) = \Pp \cap E_j(q_j, \theta_j)$.

	The third case is the complement of the other two cases, that is, the $j$-eh ellipse covers at least three points, and there is an equivalent solution with three points on its border. 
	As for every triplet of points, $S_j^{(3)}$ contains every possible center and angle of rotation that puts the three points on the ellipse's border, for sure the equivalent solution is in $S_j^{(3)}$.

@@

This is the case where $|\Pp \cap E_j(q_j^*, \theta_j^*)|=1$, that is, the $j$-th ellipse only covers one point in the optimal solution $(Q^*, \Theta^*)$. 
This case is not treated by any of the previous results presented in this chapter. Nevertheless, taking this into account can be done by
considering, for all $u\in\Pp$, the possibility of having the $j$-th ellipse centered at $u$ with an angle of rotation $0$.
We do that by defining 
\begin{equation}
	S_j^{(1)} = \bigcup_{u \in \Pp} \{(u, 0)\}.
\end{equation}

\subsection{Second case}
This is the case where $|\Pp \cap E_j(q_j^*, \theta_j^*)| \ge 2$ and there is no equivalent solution that has the $j$-th ellipse with three points on its border.
This case is addressed by \autoref{lema:3pnts}, which says that $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v \in \Pp \cap E_j(q_j^*, \theta_j^*)$ on the ellipse's border, and is rotated by some angle $\theta \in \Phi_j(u,v)$.
As only one angle is needed, we define $\theta_{uv}$ as the one that makes the major-axis of the ellipse be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
Having said that, we refer to $S_j^{(2)}$ as the set of possible solutions that takes this case into account; we define it as
\begin{equation}
S_j^{(2)} = \bigcup_{\{u, v\} \subset \Pp} \{(q, \theta_{uv})\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \theta_{uv})\}.\\
\end{equation}
For a pair of points $u, v$, determining every ellipse with a fixed rotation angle that has $u$ and $v$ on its border is equivalent to determining the intersection points of two axis-parallel ellipses with the same shape parameters. This problem is discussed with great detail in \autoref{section:ellipses_intersection}.

@@

define the CLS for the $j$-th ellipse as $S_j = S_j^{(1)} \cup S_j^{(2)} \cup S_j^{(3)}$, and the set of possible solutions of an instance of MCER as
%\begin{equation}\label{eq:omega}
%\Omega(\Pp, \Ww, \Rr) = \{(Q, \Theta)\in \R^{2m}\times\R^m \colon (q_j, \theta_j) \in S_j \textnormal{ for all } j\in\{1, \dots, m\}\}.
%\end{equation}

%\begin{theorem}\label{th:mcer}
%	Let $(\Pp, \Ww, \Rr)$ be an instance of MCER, and $\Omega(\Pp, \Ww, \Rr)$ be a set of solutions defined by \autoref{eq:omega}. Then there exists an optimal solution $(Q^*, \Theta^*) \in \Omega(\Pp, \Ww, \Rr)$, and $|\Omega(\Pp, \Ww, \Rr)|=\bigO(n^{3m})$.	
%\end{theorem}
